%%%
%%% Sindhu's Outline
%%%

\section{Sindhu's Outline}

In the notes on Maximum Entropy Market Maker, Lahaie constructs a scoring rule (and its sequential form: a market maker) based on maximum entropy distributions. Here is the problem: Suppose you want to elicit sufficient statistics from a trader (or group of traders: in this latter case you want to aggregate their information). Then if you find a probability distribution that is consistent with their belief of the expected sufficient statistics, you can construct a proper scoring rule (that is, the true distribution maximizes payoff). However, the solution to this consistent distribution is not unique. Hence, to pick amongst the distributions, you could choose the one that maximizes entropy (which is a notion of uncertainty) -- intuitively, this assumes the least about the distribution generating the data. Now, it turns out that the distribution that maximizes entropy is an exponential family distribution. So, if it is known that the true probability is an exponential family distribution, eliciting just the statistics allows you to characterize the actual probability distribution.

In the prediction markets and exponential families write-up, we have shown that that the various parts of the exponential family correspond to securities, payoffs and cost in a prediction market. We have shown that a sequence of traders seeking to maximize profit will essentially be performing a MLE of the natural parameters of an exponential family, when the beliefs of the traders take the form of an exponential family distribution (it turns out that this last assumption is not necesary in light of the above result). Further, in a budget-limited setting, adversarial traders can cause limited damage and informative traders' budgets grow in expectation over time when trading in multiple markets. The budget-limited results have the following issues. First, the movement of the share vector is not completely justified. Second, as it stands currently, the growth in budget is shown in expectation over a belief distribution of the informative trader, and this distribution is assumed to be an exponential family (this may be fixable).


So broadly, the outline is as follows: The main goal is to construct a prediction market that aggregates information from traders to determine the sufficient statistics of some unknown distribution. First, we can show that in a thin market with a single trader this can be done by constructing a (proper) scoring rule using a maximum entropy approach. This approach can then be extended to define a market scoring rule for a prediction market to aggregate information from multiple traders. This follows from the duality that exists between the maximum entropy approach and exponential families. We know that the updates to the mean parameters in a Bayesian setting are a convex combination of the empirical mean and the prior.  We can then show that the share vectors of this prediction market follow the Bayesian updates of the mean parameters when each trader treats the current market state as the prior and his beliefs as the empirical mean. Since we can interpret the share vector as the natural parameters of the exponential family, the updates essentially happen in a dual space.  This process of mapping to a dual space to perform an update is reminiscent of the online mirror descent algorithm; what exactly is the mapping? Also, we would like to analyze the prediction market so defined, when the traders are budget limited.  Is the step size of the algorithm somehow related to the budgets of the traders?